NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2019-02-08 Manuscript/manuscriptPS.tex
Update manuscriptPS.tex

  reported in the experiments by Roux et al.~\cite{roux90}.
  The simulation details are given in the supplementary information.

@@

\begin{tabular}{l c c c c c c c c c }
  lipid/counter-ions & force field for lipids / ions & [CaCl$_2$]\,(M)  &  \footnote{Number of lipid molecules with largest mole fraction}N$_{\rm l}$   &  \footnote{Number of water molecules}N$_{\rm w}$   & \footnote{Number of additional cations}N$_{\rm c}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns) & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns) &   \footnote{Reference for simulation files}files\\

@@

    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13} &0 & 250:50 & 11207 & 0  & 298  & 200 & 180   & \cite{POPC5POPS1noCaClCHARMM}  \\
    POPC:POPS (5:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13} &0 & 110:22 & 4620  & 0  & 298  & 500 & 100 & \cite{charmm36pops+83popcT298Kpiggot}  \\
    POPC:POPS (5:1)/Na$^+$ & CHARMM36 \cite{klauda10,venable13} &0 & 110:22 & 4620  & 0  & 298  & 500 & 100 & \cite{charmm36pops+83popcT298KpiggotSODIUM}  \\
    POPC:POPS (5:1)        & CHARMM36 \cite{klauda10,venable13,kim16}  & 0.26 & 250:50  & 11190  & 53  & 298  & 200 & 180 & \cite{POPC5POPS1withCaClCHARMM}   \\
    POPC:POPS (5:1)        & CHARMM36 \cite{klauda10,venable13,kim16}  & 1.06 & 250:50  & 11174  & 214  & 298  & 200 & 180  & \cite{POPC5POPS1with1MCaClCHARMM}  \\
    POPC:POPS (1:1)/K$^+$  & CHARMM36 \cite{klauda10,venable13}        & 0    & 150:150 & 10785    & 0  & 298  & 200 & 180   & \cite{POPC1POPS1noCaClCHARMM}  \\

@@

    POPC:POPS (1:0)        & MacRog \cite{maciejewski14} &0    & 120:0  & 5120 & 0    & 298  & 200 & 150 & \cite{macrogPOPC298K}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} &0    & 120:24 & 5760 & 0    & 298  & 400 & 250 & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} & 0.10 & 120:24 & 5760 & 10   & 298  & 600 & 300 & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} & 0.30 & 120:24 & 5760 & 31   & 298  & 600 & 300  & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} & 1.00   & 120:24 & 5760 & 104  & 298  & 600 & 300  & \cite{POPCpopsMACROG}  \\
    POPC:POPS (5:1)/K$^+$  & MacRog \cite{maciejewski14} & 3.00   & 120:24 & 5760 & 311  & 298  & 600 & 300  & \cite{POPCpopsMACROG}  \\

@@

@@

    POPC:POPS (5:1)/K$^+$  & Lipid14/17 \cite{dickson14,gould18}  & 0      & 120:24 & 5760 & 0   & 298  & 500 & 200 & \cite{POPCpopsLIPID17withKCI}  \\
    POPC:POPS (5:1)/Na$^+$  & Lipid14/17 \cite{dickson14,gould18} & 0      & 120:24 & 5760 & 0   & 298  & 500 & 200 & \cite{POPCpopsLIPID17withNaCI}  \\
    POPC:POPS (5:1)         & Lipid14/17 \cite{dickson14,gould18} &0.50    & 120:24 & 5760 & 52   & 298  & 300 & 200 & \cite{POPCpopsLIPID17withCaCl}  \\
    POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}        &1.00    & 120:24 & 5760 & 104   & 298  & 300 & 200 & \cite{POPCpopsLIPID17withCaCl}  \\
    POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}        &2.00    & 120:24 & 5760 & 208   & 298  & 300 & 200 & \cite{POPCpopsLIPID17withCaCl}  \\
    POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}        &3.00    & 120:24 & 5760 & 311   & 298  & 300 & 200 & \cite{POPCpopsLIPID17withCaCl}  \\
    POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}        &4.00    & 120:24 & 5760 & 415   & 298  & 300 & 200 & \cite{POPCpopsLIPID17withCaCl}  \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18}  & 0      & 60:12 & 3600  & 0   & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.08   & 60:12 & 3561  & 5   & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.13   & 60:12 & 3561  & 8   & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.20   & 60:12 & 3561  & 13  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.41   & 60:12 & 3522  & 26  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\
    POPC:POPS (5:1)/Na$^+$ & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.62   & 60:12 & 3483  & 39  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series}   \\

@@

    POPC:POPS (4:1)/Na$^+$  & Berger \cite{tieleman99,mukhopadhyay04}  & 0   & 102:26 & 4290 & 0   & 310  & 120 & 80 & \cite{bergerPOPSPOPC4:1mixtureT310K}  \\
    POPC:POPS (4:1)  & Berger \cite{tieleman99,mukhopadhyay04}         & 0.102\footnote{Calculation of concetration complicated due the scaled ions. Concentration taken as reported in the delivered data.}   & 104:24 & 4306 & 24 & 310  & 300 & 100 & \cite{POPCpopsBERGERwith102mMCa}  \\
    POPC:POPS (4:1)  & Berger \cite{tieleman99,mukhopadhyay04}         & 0.715\footnote{Calculation of concetration complicated due the scaled ions. Concentration taken as reported in the delivered data.}  & 104:24 & 4306 & 72 & 310  & 300 & 100 & \cite{POPCpopsBERGERwith715mMCa}  \\
    POPC:POPS (5:1)/Na$^+$  & GROMOS-CKP \cite{??}             & 0     & 110:22 & ?     & 0  & 298  & 500 & 100 & \cite{POPCpopsGROMOSCKPwithNa}  \\
    POPC:POPS (5:1)/Na$^+$  & GROMOS-CKPM \cite{??}            & 0     & 110:22 & ?     & 0  & 298  & 500 & 100 & \cite{POPCpopsGROMOSCKPMwithNa}  \\

>>>>

  reported in the experiments by Roux et al.~\cite{roux90}.  Notation 2$\times$[time] indicates that more than two independent MD runs was conducted. The simulation details are given in the supplementary information. 

@@

\begin{tabular}{lccccccccc}
lipid/counter-ions  & force field for lipids / ions  & {[}CaCl$_{2}${]}\,(M)  & \footnote{Number of lipid molecules with largest mole fraction}N$_{{\rm l}}$  & \footnote{Number of water molecules}N$_{{\rm w}}$  & \footnote{Number of additional cations}N$_{{\rm c}}$  & \footnote{Simulation temperature}T (K)  & \footnote{Total simulation time}t$_{{\rm sim}}$(ns)  & \footnote{Time used for analysis}t$_{{\rm anal}}$ (ns)  & \footnote{Reference for simulation files}files\tabularnewline

@@

POPC:POPS (5:1)/K$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 250  & 11207  & 0  & 298  & 200  & 180  & \cite{POPC5POPS1noCaClCHARMM} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 110  & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \cite{charmm36pops+83popcT298Kpiggot} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 110 & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \cite{charmm36pops+83popcT298KpiggotSODIUM} \tabularnewline
POPC:POPS (5:1)  & CHARMM36 \cite{klauda10,venable13,kim16}  & 0.26  & 250 & 11190  & 53  & 298  & 200  & 180  & \cite{POPC5POPS1withCaClCHARMM} \tabularnewline
POPC:POPS (5:1)  & CHARMM36 \cite{klauda10,venable13,kim16}  & 1.06  & 250 & 11174  & 214  & 298  & 200  & 180  & \cite{POPC5POPS1with1MCaClCHARMM} \tabularnewline
POPC:POPS (1:1)/K$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 150  & 10785  & 0  & 298  & 200  & 180  & \cite{POPC1POPS1noCaClCHARMM} \tabularnewline

@@

POPC:POPS (1:0)  & MacRog \cite{maciejewski14}  & 0  & 120 & 5120  & 0  & 298  & 200  & 150  & \cite{macrogPOPC298K} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0  & 120 & 5760  & 0  & 298  & 400 \todo{lenght wrong? Check zenodo} & 250 \todo{lenght wrong? Check zenodo} &  \todo{this ref is to trajectory with CA}\cite{POPCpopsMACROG}\tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0.10  & 120  & 5760  & 10  & 298  & 600  & 300  & \cite{POPCpopsMACROG} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0.30  & 120  & 5760  & 31  & 298  & 600  & 300  & \cite{POPCpopsMACROG} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 1.00  & 120 & 5760  & 104  & 298  & 600  & 300  & \cite{POPCpopsMACROG} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 3.00  & 120 & 5760  & 311  & 298  & 600 & 300 & \cite{POPCpopsMACROG}\tabularnewline

@@

POPC:POPS (5:1)/K$^{+}$  & Lipid14/17 \cite{dickson14,gould18}  & 0  & 120  & 5760  & 0  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withKCI} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18}  & 0  & 120 & 5760  & 0  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withNaCI} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}  & 0.50  & 120 & 5760  & 52  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}  & 1.00  & 120  & 5760  & 104  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}  & 2.00  & 120  & 5760  & 208  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}  & 3.00  & 120 & 5760  & 311  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18}  & 4.00  & 120  & 5760  & 415  & 298  & 2$\times$500  & 2$\times$200  & \cite{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18}  & 0  & 60 & 3600  & 0  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.08  & 60  & 3561  & 5  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.13  & 60  & 3561  & 8  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.20  & 60 & 3561  & 13  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.41  & 60 & 3522  & 26  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18,smith94,dang06}  & 0.62  & 60 & 3483  & 39  & 298  & 1000  & 1000  & \cite{lipid17_cacl_series} \tabularnewline

@@

POPC:POPS (4:1)/Na$^{+}$  & Berger \cite{tieleman99,mukhopadhyay04}  & 0  & 102 & 4290  & 0  & 310  & 120  & 80  & \cite{bergerPOPSPOPC4:1mixtureT310K} \tabularnewline
POPC:POPS (4:1)  & Berger \cite{tieleman99,mukhopadhyay04}  & 0.102\footnote{\label{noteBerger}Calculation of concetration complicated by the
usage scaled ions. Concentration taken as reported in the delivered
data.}  & 104  & 4306  & 24  & 310  & 300  & 100  & \cite{POPCpopsBERGERwith102mMCa} \tabularnewline
POPC:POPS (4:1)  & Berger \cite{tieleman99,mukhopadhyay04}  & 0.715\textsuperscript{\ref{noteBerger}}  & 104 & 4306  & 72  & 310  & 300  & 100  & \cite{POPCpopsBERGERwith715mMCa} \tabularnewline

@@

POPC:POPS (5:1)/Na$^{+}$  & GROMOS-CKP \cite{??}  & 0  & 110 & ?  & 0  & 298  & 2$\times$500  & 2$\times$100  & \cite{POPCpopsGROMOSCKPwithNa} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & GROMOS-CKPM \cite{??}  & 0  & 110 & ?  & 0  & 298  & 2$\times$500  & 2$\times$100  & \cite{POPCpopsGROMOSCKPMwithNa} \tabularnewline
